Synthetic Population for Bogota

### 2023-03-22 code/synthetic_population/bogota_synth_pop.qmd
Use arrow and remove unused code. Ref #128

```{r}
library(rsample)
library(tidyverse)
library(summarytools)

@@

@@

rts <- bt |> filter(!is.na(trip_mode)) |> group_by(trip_mode) |> summarise(n = n()) |> mutate(raw_trip_freq = round(n / sum(n) * 100, 1))
rss <- bt |> filter(!is.na(stage_mode)) |> group_by(stage_mode) |> summarise(n = n()) |> mutate(raw_stage_freq = round(n / sum(n) * 100, 1))

et <- bt %>% mutate(pw = round(participant_wt - 1))
exp1 <- et  |> filter(pw > 0) |> uncount(pw, .id = "pid")
exp2 <- et  |> filter(pw > 0) |> filter(pw == 0) %>% mutate(pid = 1)

print(dfSummary(exp1 |> filter(age != 9999),
                varnumbers   = FALSE, 
                valid.col    = FALSE, 
                graph.magnif = 0.76),
      method = 'render')

ets <- exp1 |> filter(!is.na(trip_mode)) |> group_by(trip_mode) |> summarise(n = n()) |> mutate(exp_trip_freq = round(n / sum(n) * 100, 1))
ess <- exp1 |> filter(!is.na(stage_mode)) |> group_by(stage_mode) |> summarise(n = n()) |> mutate(exp_stage_freq = round(n / sum(n) * 100, 1))

ts <- full_join(rts, ets)
ss <- left_join(rss, ess)

st <- rsample::training(rsample::initial_split(exp1, prop = 0.1, strata = trip_mode))
ss <- rsample::training(rsample::initial_split(exp1, prop = 0.1, strata = stage_mode))

@@

print(dfSummary(ss,
                varnumbers   = FALSE, 
                valid.col    = FALSE, 
                graph.magnif = 0.76),
      method = 'render')
# 
# st |> filter(!is.na(trip_mode)) |> group_by(trip_mode) |> summarise(n = n()) |> mutate(exp_trip_freq = round(n / sum(n) * 100, 1))
# 
# rd <- plyr::rbind.fill(exp1, exp2) %>% arrange(hh_id, person_id, trip_id)

@@

>>>>

```{r}
library(rsample)
library(tidyverse)
library(summarytools)
library(arrow)

@@

## Summary without weights

@@

# rts <- bt |> filter(!is.na(trip_mode)) |> group_by(trip_mode) |> summarise(n = n()) |> mutate(raw_trip_freq = round(n / sum(n) * 100, 1))
# rss <- bt |> filter(!is.na(stage_mode)) |> group_by(stage_mode) |> summarise(n = n()) |> mutate(raw_stage_freq = round(n / sum(n) * 100, 1))
# 
# ets <- exp1 |> filter(!is.na(trip_mode)) |> group_by(trip_mode) |> summarise(n = n()) |> mutate(exp_trip_freq = round(n / sum(n) * 100, 1))
# ess <- exp1 |> filter(!is.na(stage_mode)) |> group_by(stage_mode) |> summarise(n = n()) |> mutate(exp_stage_freq = round(n / sum(n) * 100, 1))
# 
# ts <- full_join(rts, ets)
# ss <- left_join(rss, ess)

# 
# st |> filter(!is.na(trip_mode)) |> group_by(trip_mode) |> summarise(n = n()) |> mutate(exp_trip_freq = round(n / sum(n) * 100, 1))
# 
# rd <- plyr::rbind.fill(exp1, exp2) %>% arrange(hh_id, person_id, trip_id)

## Summary with weights - expanded travel survey

```{r, results='asis'}

exp1 <- read_parquet("../../data/local/bogota/exp_trips.parquet")
# Remove undefined ages
exp1 <- exp1 |> filter(age != 9999)

# exp2 <- et  |> filter(pw > 0) |> filter(pw == 0) %>% mutate(pid = 1)

print(dfSummary(exp1,
                varnumbers   = FALSE, 
                valid.col    = FALSE, 
                graph.magnif = 0.76),
      method = 'render')

## Summary of sampled travel survey - with trip_mode strata

```{r, results='asis'}
st <- rsample::training(rsample::initial_split(exp1, prop = 0.1, strata = trip_mode))

@@

@@

## Summary of sampled travel survey - with stage_mode strata

```{r, results='asis'}
ss <- rsample::training(rsample::initial_split(exp1, prop = 0.1, strata = stage_mode))
print(dfSummary(ss,
                varnumbers   = FALSE, 
                valid.col    = FALSE, 
                graph.magnif = 0.76),
      method = 'render')
